Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-27 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

\footnote{\yutsung{The word ''cryptodeterminism'' is used by Peres~\cite{peres1995quantum}
without a clear definition. I tried to check its meaning from other
sources.

In~\cite{PeresRon1988}, Peres and Ron defined
\begin{quote}
We now introduce the cryptodeterministic hypothesis: It is possible
to specify all the details of a preparation, so that the result of
any measurement becomes completely deterministic.
\end{quote}
Unfortunately, Google Book cannot preview all pages, and the InterLibrary
Loan hasn't finished my request, yet...

In~\cite{Atmanspacher2014}, Atmanspacher defined 
\begin{quote}
...one might paraphrase the deterministic yet non-determinable behavior
of such systems as ``cryptodeterminism''...
\end{quote}
where ``deterministic'' and ``determinable'' is defined in the
same section as 
\begin{quote}
The recent creation of the term ``deterministic chaos'' expresses
the tension between ontic (hidden) lawfulness and epistemic (apparent)
irregularity in chaotic system. Our description of the underlying
laws of nature, e.g. by differential equations governing the dynamics
of such systems, is no doubt deterministic, but their observable behavior
is everything but determinable (in the sense of measurable, computable,
or predictable) with arbitrary precision....
\end{quote}
Is Atmanspacher's usage consistent with Peres' and ours here?}}Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.

@@

\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
the prefect prediction, a cryptodeterministic measure can model the
belief of events which has already happened. For example, if we tossed
the coin in example~\ref{ex1}, and saw $HH$, our belief of which
event has happened can be model by the following example.
\begin{equation}
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & 0\\
\bar{\mu}(\{HH\}) & = & 1\\
\bar{\mu}(\{HT\}) & = & 0\\
\bar{\mu}(\{TH\}) & = & 0\\
\bar{\mu}(\{TT\}) & = & 0\\
\bar{\mu}(\{HH,HT\}) & = & 1\\
\bar{\mu}(\{HH,TH\}) & = & 1\\
\bar{\mu}(\{HH,TT\}) & = & 1
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & 0\\
\bar{\mu}(\{HT,TT\}) & = & 0\\
\bar{\mu}(\{TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH\}) & = & 1\\
\bar{\mu}(\{HH,HT,TT\}) & = & 1\\
\bar{\mu}(\{HH,TH,TT\}) & = & 1\\
\bar{\mu}(\{HT,TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & 1
\end{array}\end{array}
\end{equation}
\end{example}

\noindent The ability to predict classical events unambiguously rather
than probabilistic inspired Einstein, Podolsky, and Rosen to ask whether
quantum mechanics have any chance to be improved and predict in the
same way~\cite{EPR1935,peres1995quantum}. This question can be formulated
by whether the quantum mechanics could be modeled by quantum cryptodeterministic
measures.

>>>>

Although a real or interval-valued probability measure could model
whether we believe an event will happen or not, the classical world
could be modeled in a simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic\footnote{The word ''cryptodeterminism'' is used by Peres which means
\begin{quote}
We now introduce the cryptodeterministic hypothesis: It is possible
to specify all the details of a preparation, so that the result of
any measurement becomes completely deterministic.
\end{quote}
in~\cite{PeresRon1988}, and
\begin{quote}
... any purported cryptodeterministic theory which would attribute
a definite result to each quantum measurement, and still reproduce
the statistical properties of quantum theory ...
\end{quote}
in~\cite{Peres1991,peres1995quantum}.} measure defined as follow.

@@

\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
the prefect prediction, a cryptodeterministic measure can model the
belief of events which has already happened. For example, if we tossed
the coin in example~\ref{ex1}, and saw $HH$, our belief of which
event has happened is represented by the following example.
\begin{equation}
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & 0\\
\bar{\mu}(\{HH\}) & = & 1\\
\bar{\mu}(\{HT\}) & = & 0\\
\bar{\mu}(\{TH\}) & = & 0\\
\bar{\mu}(\{TT\}) & = & 0\\
\bar{\mu}(\{HH,HT\}) & = & 1\\
\bar{\mu}(\{HH,TH\}) & = & 1\\
\bar{\mu}(\{HH,TT\}) & = & 1
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & 0\\
\bar{\mu}(\{HT,TT\}) & = & 0\\
\bar{\mu}(\{TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH\}) & = & 1\\
\bar{\mu}(\{HH,HT,TT\}) & = & 1\\
\bar{\mu}(\{HH,TH,TT\}) & = & 1\\
\bar{\mu}(\{HT,TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & 1
\end{array}\end{array}
\end{equation}
\end{example}

\noindent The ability to predict classical events unambiguously rather
than probabilistic inspired Einstein, Podolsky, and Rosen to ask whether
quantum mechanics have any chance to be improved and predict in the
same way~\cite{EPR1935,peres1995quantum,544199,Mermin2007}. This
question can be formulated by whether the quantum mechanics could
be modeled by quantum cryptodeterministic measures.
